---
title: "model_coefs"
author: "Aodhan Hayter"
date: "12/3/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(caret)
library(RANN)
library(missForest)
library(ggplot2)
```

```{r}
compare_factor_levels <- function(train, test) {
  train_levels <- train %>%
    select_if(is.character) %>%
    mutate_all(.funs = factor) %>%
    map(.f = levels)

  test_levels <- test %>%
    select_if(is.character) %>%
    mutate_all(.funs = factor) %>%
    map(.f = levels)

  data <- data.frame(
    variables = names(train_levels),
    identical_levels = 0
  )

  for (i in 1:nrow(data)) {
    data$identical_levels[i] <- ifelse(setequal(train_levels[[i]], test_levels[[i]]), "yes", "no")
  }

  print(data)
}

test_missing <- function(data) {
  data %>%
    mutate_all(.funs = is.na) %>%
    summarise_all(.funs = sum) %>%
    t() %>%
    as.data.frame() %>%
    filter(V1 > 0)
}

calc_total_SF <- function(firstSF, secondSF, bsmtSF) {
  first <- if_else(is.na(firstSF), 0, firstSF)
  second <- if_else(is.na(secondSF), 0, secondSF)
  bsmt <- if_else(is.na(bsmtSF), 0, bsmtSF)
  
  first + second + bsmt
}

calc_total_bath <- function(full, half, bsmt_full, bsmt_half) {
  f <- if_else(is.na(full), 0, full)
  h <- if_else(is.na(half), 0, half)
  bf <- if_else(is.na(bsmt_full), 0, bsmt_full)
  bh <- if_else(is.na(bsmt_half), 0, bsmt_half)
  
  f + h + bf + bh
}

clean_data <- function(data) {
  data %>%
    select(-Utilities) %>%
    mutate(
      TotalSF = calc_total_SF(`1stFlrSF`, `2ndFlrSF`, TotalBsmtSF),
      TotalBath = calc_total_bath(FullBath, HalfBath, BsmtFullBath, BsmtHalfBath),
      RoofMatl = factor(RoofMatl),
      MSZoning = if_else(is.na(MSZoning), "RL", MSZoning) %>% factor(),
      OverallQual = factor(OverallQual),
      PoolQC = factor(PoolQC) %>% addNA(),
      ExterQual = factor(ExterQual),
      KitchenQual = if_else(is.na(KitchenQual), "TA", KitchenQual) %>% factor(),
      Foundation = factor(Foundation),
      BsmtQual = factor(BsmtQual) %>% addNA(),
      BsmtFinType1 = if_else(is.na(BsmtFinType1), "No Basement", BsmtFinType1) %>% factor(),
      GarageFinish = if_else(is.na(GarageFinish), "No Garage", GarageFinish) %>% factor(),
      Neighborhood = factor(Neighborhood),
      MasVnrType = factor(MasVnrType) %>% addNA(),
      SaleType = if_else(is.na(SaleType), "WD", SaleType) %>% factor(),
      GarageType = if_else(is.na(GarageType), "No Garage", GarageType) %>% factor(),
      SaleCondition = factor(SaleCondition),
      FireplaceQu = if_else(is.na(FireplaceQu), "No Fireplace", FireplaceQu) %>% factor(),
      BsmtExposure = if_else(is.na(BsmtExposure), "No Basement", BsmtExposure) %>% factor(),
      Exterior1st = factor(Exterior1st),
      Exterior2nd = factor(Exterior2nd),
      Heating = factor(Heating),
      GarageYrBlt = factor(GarageYrBlt) %>% addNA(),
      BsmtFinType2 = if_else(is.na(BsmtFinType2), "No Basement", BsmtFinType2) %>% factor(),
      YearBuilt = factor(YearBuilt),
      # these are numerical variables that are missing
      MasVnrArea = if_else(is.na(MasVnrArea), median(data$MasVnrArea, na.rm = T), MasVnrArea),
      LotFrontage = if_else(is.na(LotFrontage), median(data$LotFrontage, na.rm = T), LotFrontage),
      GarageCars = if_else(is.na(GarageCars), median(data$GarageCars, na.rm =T), GarageCars),
      GarageArea = if_else(is.na(GarageArea), median(data$GarageArea, na.rm =T), GarageArea),
      BsmtFinSF1 = if_else(is.na(BsmtFinSF1), median(data$BsmtFinSF1, na.rm =T), BsmtFinSF1),
      BsmtFinSF2 = if_else(is.na(BsmtFinSF2), median(data$BsmtFinSF2, na.rm =T), BsmtFinSF2),
      TotalBsmtSF = if_else(is.na(TotalBsmtSF), median(data$TotalBsmtSF, na.rm =T), TotalBsmtSF),
    )
}
```

```{r}
to_plot <- c("OverallQual", "PoolQC", "TotalSF", "TotalBath", "RoofMatl", "MSZoning", "GrLivArea", "GarageCars", "GarageArea", "TotalBsmtSF", "1stFlrSF", "FullBath", "TotRmsAbvGrd", "YearBuilt", "KitchenQual", "YearRemodAdd", "Foundation", "MasVnrArea", "Fireplaces", "ExterQual", "BsmtQual", "BsmtFinType1", "GarageFinish", "Neighborhood", "BsmtFinSF1", "MasVnrType", "SaleType", "GarageType", "SaleCondition", "FireplaceQu", "LotFrontage", "BsmtExposure", "2ndFlrSF", "WoodDeckSF", "OpenPorchSF", "Heating", "BsmtFinType2", "BsmtFinSF2")
```

# Training Data

```{r}
d_train <- read_csv("train.csv")
```

# Clean Training Data

```{r}
d_train_clean <- d_train %>%
  select(-Id) %>%
  clean_data()

to_train <- d_train_clean[c("SalePrice", to_plot)]
train_dummies <- dummyVars(~., data = to_train, fullRank = T)
train_dummy_set <- predict(train_dummies, newdata = to_train)
train_complete <- preProcess(train_dummy_set, "medianImpute") %>% predict(train_dummy_set)
```

```{r}
train_corr_mat <- train_complete %>%
  as_tibble() %>%
  cor() %>%
  round(2)
sale_price_corr <- as.data.frame(train_corr_mat[, c("SalePrice")])
colnames(sale_price_corr) <- c("corr")
sale_price_corr <- rownames_to_column(sale_price_corr, var = "coef")
```

# Correlations

```{r}
(top_corr <- sale_price_corr %>%
  mutate(corr = abs(corr)) %>%
  filter(abs(corr) >= 0.3 & abs(corr) <= 0.9) %>%
  arrange(desc(corr))
)

# to_plot <- c("OverallQual", "PoolQC", "TotalSF", "TotalBath", "RoofMatl", "MSZoning", "GrLivArea", "GarageCars", "GarageArea", "TotalBsmtSF", "1stFlrSF", "FullBath", "TotRmsAbvGrd", "YearBuilt", "KitchenQual", "YearRemodAdd", "Foundation", "MasVnrArea", "Fireplaces", "GarageYrBlt", "ExterQual", "BsmtQual", "BsmtFinType1", "GarageFinish", "Neighborhood", "BsmtFinSF1", "MasVnrType", "SaleType", "GarageType", "SaleCondition", "FireplaceQu", "LotFrontage", "BsmtExposure", "2ndFlrSF", "WoodDeckSF", "OpenPorchSF", "Exterior1st", "Exterior2nd", "Heating", "BsmtFinType2", "BsmtFinSF2")
```

# Verify Training Data

```{r}
(test_missing(d_train_clean[to_plot]))
```

# Testing Data

```{r}
d_test <- read_csv("test.csv")
```

# Clean Testing Data
```{r}
d_test_clean <- d_test %>% clean_data()

d_test_clean$PoolQC <- factor(d_test_clean$PoolQC, levels = d_train_clean$PoolQC %>% levels()) %>% addNA()
d_test_clean$RoofMatl <- factor(d_test_clean$RoofMatl, levels = d_train_clean$RoofMatl %>% levels())
d_test_clean$Exterior1st<- factor(d_test_clean$Exterior1st, levels = d_train_clean$Exterior1st %>% levels())
d_test_clean$Exterior2nd<- factor(d_test_clean$Exterior2nd, levels = d_train_clean$Exterior2nd%>% levels())
d_test_clean$Heating<- factor(d_test_clean$Heating, levels = d_train_clean$Heating%>% levels())


to_test <- d_test_clean[to_plot]
test_dummies <- dummyVars(~., data = d_test_clean, fullRank = T)
test_dummy_set <- predict(test_dummies, newdata = d_test_clean)
test_complete <- preProcess(test_dummy_set, "medianImpute") %>% predict(test_dummy_set)

```

# Verify Test Data

```{r}
(test_missing(d_test_clean[to_plot]))
```

# Compare Factor Levels
```{r}
compare_factor_levels(d_train, d_test) %>% filter(identical_levels == "no")
```
# Model Planning

y = log(SalePrice) ~ log(1stflrSF) + log(LotArea)

## Coefs to explore

- OverallQual
- GrLivArea
- GarageCars
- GarageArea
- TotalBsmtSF
- `1stFlrSF`
- ExterQualITA
- FUllBath
- TotRmsAbvGrd
- YearBuilt
- KitchenQualTA
- YearRemodAdd
- FoundationPConc
- MasVnrArea
- Fireplaces
- GarageYrBlt
- ExterQualGd
- BsmtQualTA
- BsmtFinType1GLQ
- GarageFinishUnf
- NeighborhoodNridgHt
- BsmtFinSF1
- MasVnrTypeNone
- SaleTypeNew
- GarageTypeDetchd
- SaleConditionPartial
- FoundationCBlock
- FireplaceQuGd
- LotFrontage
- NeighborhoodNoRidge
- MasVnrTypeStone
- BsmtExposureNo
- `2ndFlrSF`
- KitchenQualGd
- WoodDeckSF
- OpenPorchSF
- Exterior1stVinylSd
- Exterior2ndVinylSd
- BsmtExposureGd
- HeatingQCTA

# Plots

```{r}
for (name in to_plot) {
  print(name)
  print(ggplot(d_train, aes(d_train_clean[[name]], log(SalePrice))) +
    geom_jitter() +
    theme_minimal() +
    geom_smooth(method = "lm", se = F) +
    theme(axis.text.x = element_text(angle = 90, hjust = 1, size = 5)) +
    labs(
      title = str_interp("log(SalePrice) ~ ${name}"),
      x = name
    ))
}
```

```{r}
ggplot(d_train_clean, aes(log(`1stFlrSF`), log(SalePrice)))+
  geom_point(alpha = .15)+
  geom_smooth(method="lm", se = F, aes(col = Neighborhood)) +
  labs(title = "log(price) ~ log(sqft) by city")+
  theme_minimal()
```
# Modeling

```{r}
set.seed(123)

# (imp_model <- train(log(SalePrice) ~ ., data = train_complete, method = "lm"))
# imp_model %>% summary

(test_model <-
  train(
    log(SalePrice) ~
      log(TotalSF) * Neighborhood +
      RoofMatl +
      MSZoning +
      log(`1stFlrSF`) +
      `2ndFlrSF` +
      log(LotArea) +
      # LotFrontage +
      # BsmtFinSF1 +
      OverallQual +
      # GrLivArea +
      GarageCars +
      TotalBsmtSF +
      TotalBath +
      FullBath +
      YearBuilt +
      YearRemodAdd +
      Foundation +
      Fireplaces +
      KitchenQual +
      MasVnrType +
      # SaleType +
      # GarageType +
      WoodDeckSF,
      data = d_train_clean,
      method = "lm"
  ))

test_model %>% summary()
```
```{r}
rmse <- function(actual, fitted) sqrt(mean((actual - fitted)^2))

(model_rmse = rmse(log(d_train_clean$SalePrice), fitted(test_model)))
```

# Generate Predictions
```{r}
submit <- as.data.frame(test_complete) %>%
  select(Id) %>%
  mutate(SalePrice = exp(predict(imp_model, newdata = test_complete)))

submit <- d_test_clean %>%
  select(Id) %>%
  mutate(SalePrice = exp(predict(test_model, newdata = d_test_clean)))

write_csv(submit, file = "submission.csv")
```